Actuator line modeling of vertical-axis turbines

### 2016-05-02 paper.tex
Clarify that we are talking about potential flow vortex methods

Blade element based vortex line methods can be solved with reasonable
computational effort---ranging from an expense close to BEM up to that of 2-D
blade-resolved CFD. The cost is a function of the number of vortex elements,
which for free vortex methods increases at each time step, slowing down the
calculation as it marches forward in time. Vortex methods can resolve more flow
details than BEM. However, since the flow is governed by the Laplace equation,
nonlinear effects such as the turbulent transport will not be included, which we
have determined in experiments to be the same order of magnitude as the mean
vertical advection.

>>>>

Blade element based vortex line methods can be solved with reasonable
computational effort when coupled with potential flow models---ranging from an
expense close to BEM up to that of 2-D blade-resolved CFD. The cost is a
function of the number of vortex elements, which for free vortex methods may
increase at each time step, slowing down the calculation as it marches forward
in time, unless there is an additional model for vortex diffusion. Potential
flow vortex methods can resolve more flow details than BEM. However, since the
flow is governed by the Laplace equation, nonlinear effects such as the
turbulent transport will not be included, which we have determined in
experiments to be the same order of magnitude as the mean vertical advection.
